SST_patterns

### 2019-11-25 SST_patterns.Rmd
update
tips

---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document
---

@@

# GLM - Determining if a change occur in the number of signals detected at different distancces from the coastline

>>>>

---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document
---
# This script is for all the various datasets

@@

# GLM - Determining if a change occur in the number of signals detected at different distances from the coastline
# Included a table in the paper
  Table discuss/count the number of upwelling signals detected at the different distancees
